Project 2

### 2015-03-31 project2/paper/main.tex
Adding the final section

\section{Technology Used}
The simulation was built using CoffeeScript \cite{coffeescript}, using Backbone \cite{backbone}, Underscore
\cite{underscore} and jQuery \cite{jQuery} to organize code some. Code was bundled via Browserify \cite{browserify},
and minified with UglifyJS \cite{uglify}. Gulp \cite{gulp} was used as a build tool and package management was done
via NPM \cite{npm}.

\section{Current and Remaining Work}

>>>>

\section{Technology Used}
The simulation was built using CoffeeScript \cite{coffeescript}, using Backbone \cite{backbone}, Underscore
\cite{underscore} and jQuery \cite{jQuery} to organize code some. Code was bundled via Browserify \cite{browserify},
and minified with UglifyJS \cite{uglify}. Gulp \cite{gulp} was used as a build tool and package management was done
via NPM \cite{npm}. Geo-mapping was done via Leaflet \cite{leaflet}.

\section{Current and Remaining Work}
Currently, the app is simply mapping stations and labeling them. The entirety of data analysis is complete, and can be
viewed within the \texttt{queries} directory, along with the \texttt{utils}. A few data files are strewn about the
codebase as well. The WMATA API query code is stored within the \texttt{wmata} folder.

I have also copied some code over from the first project since it will be applicable, such as a discrete event queue.
However, the \texttt{Track} class remains to be written and is integral to the application. Furthermore, the actual
train scheduling algorithm itself needs to be written.
